An Authoritative Adventure

### 2022-12-21 article.tex
Fixed typo in "\listparagraph" example

\subsubsection{Hanging Indent Features}
The |listparagraph| format allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:

>>>>

\subsubsection{Hanging Indent Features}
The |\listparagraph| format allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:
